Tracing the Stellar Halos of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-06-29 draft/paper1_rachel.tex
Edit 1-D profile selection 1

    For each cut-out, to overcome the \texttt{hscPipe} ``over-deblending'' issue, 
    we use a customized procedure to detect and aggressively mask out
    neighbouring objects. 
    Furthermore, \texttt{hscPipe} tends to over-subtract the background around 
    bright objects. 
    To improve the background subtraction, we first aggressively mask 
    out all objects (including the central massive galaxy), and derive an 
    empirical background correction using \texttt{SExtractor}.
\rachel{Need to describe what settings were used and, more importantly, how these were validated.  Otherwise there is no reason to trust them over the \texttt{hscPipe} results!  You state below that you've tested this procedure, but without enough information for readers to judge.  Perhaps a key plot or two could go in the appendix?}
Then, we run \texttt{Ellipse} on the background-corrected, masked cut-outs 
    following the methodology of \citet{Li2012}. 
    In short, we first fit each isophote using a free centroid and shape 
    (ellipticity and position angle). 
    We then fix the centroid (using the mean flux-weighted centroid) and estimate
    the mean ellipticity and position angles of all isophotes. 
    Finally, we extract a 1-D surface brightness profile along the major axis using 
    the mean ellipticity and position angle. 
    We correct these surface brightness profiles for Galactic extinction and 
    cosmological dimming, and integrate them to various radii to get the luminosity 
    within different physical (elliptical) apertures. 
    Fig~\ref{fig:ellipse} shows an example of the 1-D surface brightness and 
    ellipticity profile for a massive galaxy at $z{\sim}0.2$ and also highlights 
    a few isophotes.

>>>>

    For each cut-out, to overcome the \texttt{hscPipe} ``over-deblending'' issue, 
    we use a customized procedure to detect and aggressively mask out
    neighbouring objects. 
    Furthermore, \texttt{hscPipe} tends to over-subtract the background around 
    bright objects. 
    To improve the background subtraction, we first aggressively mask 
    out all objects (including the central massive galaxy), and derive an 
    empirical background correction using \texttt{SExtractor}.
    These procedures are described in details in Appendix~\ref{app:ellipse}. 
    We should point out that we are not using the photometric results from our 
    customized process, but simply rely on them for improved local background model
    and appropriate object mask.

    Then, we run \texttt{Ellipse} on the background-corrected, masked cut-outs 
    following the methodology of \citet{Li2012}. 
    In short, we first fit each isophote using a free centroid and shape 
    (ellipticity and position angle). 
    We then fix the centroid (using the mean flux-weighted centroid) and estimate
    the mean ellipticity and position angles of all isophotes. 
    Finally, we extract a 1-D surface brightness profile along the major axis using 
    the mean ellipticity and position angle. 
    We correct these surface brightness profiles for Galactic extinction and 
    cosmological dimming, and integrate them to various radii to get the luminosity 
    within different physical (elliptical) apertures. 
    Fig~\ref{fig:ellipse} shows an example of the 1-D surface brightness and 
    ellipticity profile for a massive galaxy at $z{\sim}0.2$ and also highlights 
    a few isophotes.
